---
title: 'A paper'
author: 'Jake Bowers'
date: "`r format(Sys.time(), '%a %b %d %X %Y')`"
bibliography: main.bib
biblio-files: main.bib
biblio-style: authoryear-comp
biblatex: true
fontsize: 12pt
geometry: margin=1in
graphics: yes
latex_engine: xelatex
pdf_engine: xelatex
output:
  html_document:
    code_folding: hide
    toc: true
    fig_caption: true
    css: bowersarticle.css
  pdf_document:
    fig_caption: true
    fig_height: 7
    fig_width: 7
    keep_tex: yes
    latex_engine: xelatex
    citation_package: biblatex
    md_extensions: +autolink_bare_uris+tex_math_dollars
    number_sections: yes
    template: bowersarticle.latex
    includes:
        in_header:
           - defs-all.sty
---

```{r include=FALSE,echo=FALSE}
library(here)
require(knitr)
opts_chunk$set(strip.white=TRUE,
               width.cutoff=132,
               size='\\scriptsize',
               out.width='.8\\textwidth',
               ##message=FALSE, ## Uncomment for production
               ##warning=FALSE, ## Uncomment for production
               results=FALSE, ## by default no printing
               comment=NA)

options(digits=4,scipen=10)
```

\begin{abstract}

This is the abstract

\end{abstract}

# Overview and Introduction

This is why this is important. Roughly speaking, this is what we are going to
do. \cite{levitsky2018democracies} draw comparisons between Trump and other
democratically elected leaders.^[Thinking about general ideas of reproducible
workflow \parencite{bowers2016improve}.]

# Design

We will compare the voting outcomes of people who think that there should be
more immigration with people who think there should be less immigration, and
especially we wonder whether education (measured in years) moderates the
relationship between such attitudes and voting. The immigration attitudes
question was:


> Not using the booklet. Do you think the number of immigrants from foreign countries who are permitted to come to the United States to live should be [increased a lot, increased a little, left the same as it is now, decreased a little, or decreased a lot / decreased a lot, decreased a little, left the same as it is now, increased a little, or increased a lot]? For Web administration, reference to the respondent booklet was omitted. Forward/reverse response option order

```{r}
load(here("Analysis/desc.rda"))
```

## Outcomes

Of the `r sampsize` people in the study, `r proptrumpvote*100`% reported voting for Trump.

# Analysis

Figure~\ref{fig:lines} shows something important.

\begin{figure}[h!]
\centering
\includegraphics[width=.5\textwidth]{Figures/reglines.pdf}
\caption{This figure shows something.}\label{fig:lines}
\end{figure}

Table~\ref{tab:thetab} also is important.

\input{Figures/thetab.tex}

# Discussion, Conclusion


# References
